Pillar 2 - Topic Modeling

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
n_topics from 5 to 250 by 5
lables
eval = T for run on UM computer

```{r}
my_control_fast <- list(

@@

  n_topic = seq(from = 2, to = 150, by = 2)

@@

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r}

@@

#Get perplexity
topic_test <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```

###log_likelihood
```{r useless stuff}
# #my_loglikelihood function
# my_loglike <- function(model){
#   return(model@loglikelihood)
# }
# 
# #get loglikelihood
# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))

#Log likelihood:
test3 <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                               logLik_manual   = map(.x = TM_manual,   .f = logLik))

@@

###Plots
```{r}
#perplexity
plot(topic_test$n_topic, topic_test$perplex_overview)
plot(topic_test$n_topic, topic_test$perplex_manual)

@@

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```

##Distributions of best models
```{r Distributions, eval = TRUE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

@@

```
##Inspect topics
THE TOPICS ARE SUPPER STRANGE!
```{r inspect topics, eval = T}

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words, eval = TRUE}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

@@

```
##Convenience vectors for APP
```{r for convenience, eval = T}
# set seed
set.seed(1)

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
save(kw1, file="App/Recommender System/tmp_data.RDATA")#DELETE LATER
```

>>>>

```{r fast control}
my_control_fast <- list(

@@

  n_topic = seq(from = 5, to = 250, by = 5)

@@

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r perplexity function, eval = TRUE}

@@

#Get perplexity
test_perplexity <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```

###log_likelihood
```{r log likelihood, eval = TRUE}
# #my_loglikelihood function
# my_loglike <- function(model){
#   return(model@loglikelihood)
# }
# 
# #get loglikelihood
# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))

#Log likelihood:
test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                               logLik_manual   = map(.x = TM_manual,   .f = logLik))

@@

###Plots
```{r perplexity plots, eval = TRUE}
#perplexity
plot(topic_test$n_topic, topic_test$perplex_overview)
plot(topic_test$n_topic, topic_test$perplex_manual)

@@

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
##Saving filed for different sessions
```{r saving, eval = TRUE}
save(topic_model_gb, 
     file = "Output/topic_model_gb.RDATA")
```
#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

@@

```
##Inspect topics
THE TOPICS ARE SUPPER STRANGE!
```{r inspect topics, eval = FALSE}

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

@@

```
##Convenience vectors for APP
```{r for convenience}
# set seed
set.seed(1)

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```
